---
title: "Pl-CDI-III Norming Study"
subtitle: "Item-level Analysis"
author: "Grzegorz Krajewski"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
#    toc: true
#    toc_float: true
#    code_folding: hide
---

```{r setup, include=FALSE}
# Packages:
library(tidyverse)
library(Multilada)
library(ggpubr) # for many plots

# knitr chunk defaults:
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

# Latest website download:
export_date <- list.files(pattern ="_[0-9]{8}\\.csv") %>%
  str_extract("[0-9]{8}") %>% sort() %>% last()

# Data import:
read_csv(paste0("submissions_", export_date, ".csv")) -> submissions
read_csv(paste0("responses_", export_date, ".csv")) -> responses

# What should be used as item labels (definitions vs
# combination of grammatical categories and parts of definitions):
# label <- "gram_label"
label <- "definition"
```


```{r construction_types}
read_csv2("items.csv") -> items
items %>%
  mutate(q_main = gsub("[^[:alpha:]]", "", definition)) -> items # to avoid „ vs " etc. mismatches

read_csv("structures_all.csv") %>%
  select(! starts_with("typ")) %>% distinct() %>% # keep English & avoid complex-relative vs względne mismatch
  mutate(q2 = str_replace_na(q2, "")) %>%
  mutate(q_main = paste(q1, q2)) %>%
  mutate(q_main = gsub("[^[:alpha:]]", "", q_main)) %>% # to avoid „ vs " etc. mismatches
  right_join(items) %>%
  select(! starts_with("q") & ! "alternatywa") -> items

items %>% mutate(gram_label = paste(construction,
                                    str_extract(definition, "A\\. (.+)%B", group = 1),
                                    sep = " ")) %>%
          mutate(gram_label = str_replace_all(gram_label, " *NA", "")) %>%
          mutate(gram_label = if_else(gram_label == "", NA, gram_label)) %>%
          mutate(gram_label = str_replace(gram_label, " (.+)", " „\\1”")) -> items
```


```{r itemise}
# Lexicon:

cdi_itemise_oneCheckboxGroup(responses, "word", items) -> lex_responses
# Add IDs with no items checked, not included in the above output:
submissions %>% filter(! id %in% lex_responses$id) %>% select(id, end_date) %>%
  group_by(id, end_date) %>% group_modify(~ {
    items %>% filter(type == "word") %>% group_by(category) %>% mutate(item_id = row_number()) %>%
      add_column(response = 0, id = .x$id, end_date = .x$end_date)
  }) %>% bind_rows(lex_responses) -> lex_responses


# Alternatives:

cdi_itemise_checkboxAlt(responses, "alternatives", items) %>%
  rename(response = "answer2") %>%
  select(-answer1) -> alt_responses
# One submission (MZ4ff15UPqUXBdp5Fm6ek) without any alternatives saved... (check similar case in the pilot).
# Add MZ4ff15UPqUXBdp5Fm6ek, not included in the above output:
submissions %>% filter(! id %in% alt_responses$id) %>% select(id, end_date) %>%
  group_by(id, end_date) %>% group_modify(~ {
    items %>% filter(type == "alternatives") %>% group_by(category) %>% mutate(item_id = row_number()) %>%
      add_column(response = 0, id = .x$id, end_date = .x$end_date)
  }) %>% bind_rows(alt_responses) -> alt_responses


# Direct questions:

cdi_itemise_radio(responses, "yesNo", items) %>%
  rename(response = "answer") %>%
  mutate(response = if_else(response == 1, 1, 0)) -> direct_responses
```


## Grammar items difficulties by age

We bind together complexity alternatives and direct questions
and we calculate difficulties by age.

```{r diff_grammar_age}
bind_rows(alt_responses, direct_responses) %>%
  right_join(submissions[submissions$age_range,]) -> gram_responses
(
gram_responses %>%
  group_by(.data[[label]], construction, age) %>% summarise(difficulty = mean(response)) -> diff_gram
)
submissions %>% filter(age_range) %>% group_by(age) %>% summarise(N = n())
```


Below are barplots of difficulty by age with binomial smoothing.

```{r diff_grammar_age_plot}
# gram_responses %>% group_by(.data[[label]]) %>%
#       group_map(~ {
#         ggplot(.x) +
#           aes(age, response) +
#           stat_summary(fun = "mean", geom = "bar") +
#           geom_smooth(method = "glm", formula="y~x", method.args=list(family="binomial")) +
#           labs(x = "Age (months)", y = "Checked", title = .y) +
#           theme(plot.title = element_text(size = 6)) +
#           ylim(0, 1)
#       }) -> gram_diff_plots
# ggarrange(plotlist = gram_diff_plots, nrow = 4, ncol = 6)

gram_responses %>% ggplot(aes(age, response)) +
  stat_summary(fun = "mean", geom = "bar") +
  geom_smooth(method = "glm", formula="y~x", method.args=list(family="binomial")) +
  labs(x = "Age (months)", y = "Checked") +
  ylim(0, 1) +
  facet_wrap(as.formula(paste("~", label))) +
  theme(strip.text = element_text(size = 6)) 
```


```{r diff_grammar_age_stats}
gram_responses %>% group_by(.data[[label]]) %>%
        group_modify(~ {
                glm(response ~ age, family = binomial, .x) -> item_model
                summary(item_model)$coefficients["age", ] -> age_estimation
                cbind(data.frame(age_deviance = item_model$deviance, age_aic = item_model$aic),
                      age_coefficient = age_estimation[1], age_pvalue = age_estimation[4])
        }) -> gram_item_age
colnames(gram_item_age)[1] <- label
gram_item_age
```


```{r diff_grammar_age_predicted}
gram_responses %>% group_by(.data[[label]]) %>%
        group_modify(~ {
                glm(response ~ age, family = binomial, .x) -> item_model
                data.frame(t(predict(item_model,
                                     data.frame(age=min(.x$age) : max(.x$age)),
                                     type = "response"))) -> pred
                colnames(pred) <- paste("m", min(.x$age) : max(.x$age), sep = "_")
                pred
        }) -> gram_item_age_predicted
colnames(gram_item_age_predicted)[1] <- label
gram_item_age_predicted
```


## Selecting for WS-Grammar pilot

For matching & merging with the pilot items make sure `label` is set to `"definition"`
(it's `"`r label`"` now). Change and rerun if needed.

```{r ws_selection_prep}
if(label != "definition") knitr::knit_exit()
thres <- .6
m <- 34
```

Grammar items that had predicted difficulty at the age of `r m` months
above `r thres` (as checked on data from Oct 15th 2024):

```{r ws_selection}
(gram_item_age_predicted %>% filter(.data[[paste0("m_", m)]] > thres) %>%
  pull(.data[[label]]) %>% sort() -> selected)
items %>% filter(.data[[label]] %in% selected) -> selected_items
# gram_responses %>% filter(.data[[label]] %in% selected) -> gram_responses
# gram_item_age_predicted %>% filter(m_34 > .6) %>% pull(gram_label) %>% sort()
```


```{r ws_selection_merging}
read.csv2("items_ws.csv") %>% filter(type != "sentences" |
                                     definition %in% selected_items$definition) -> ws_items
colnames(ws_items) -> ws_columns

selected_items %>% select(definition, gram_label, construction) %>%
  rename(label = "gram_label") %>% right_join(ws_items) %>%
  mutate(gram_label = if_else(is.na(label), gram_label, label),
         gram_category = if_else(is.na(construction), gram_category, construction)) %>%
  select(- label, - construction) %>% select(ws_columns) %>%
  arrange(item_id) %>% write.csv2("items_ws_new.csv", na="", quote=F, row.names=F)
```



